\bf Model Visualization Techniques for a Social Network Model

### 2018-07-26 paper.Rnw
proofing

\if0\blind
{
  \title{\bf Model Visualization Techniques for a Social Network Model}
  \author{Samantha Tyner\thanks{
    The authors gratefully acknowledge funding from the National Science Foundation Grant \# DMS 1007697. All data collection has been conducted with approval from the Institutional Review Board IRB 10-347}\hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

@@

\noindent%
{\it Keywords:} social network analysis, model visualization, dynamic networks, network visualization, network mapping, animation
\vfill

>>>>

\if0\blind
{
  \title{\bf Model Visualization Techniques for a Social Network Model}
  \author{Sam Tyner \hspace{.2cm}\\
    Department of Statistics and Statistical Laboratory, Iowa State University\\
    and \\
    Heike Hofmann\\
    Department of Statistics and Statistical Laboratory, Iowa State University}
  \maketitle
} \fi

@@

\noindent%
{\it Keywords:} social network analysis, dynamic networks, network mapping, animation, statistical graphics
\vfill
